\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}

%\newcommand{\prop}[1]{\lbrack \! \lbrack #1 \rbrack \! \rbrack}

\title{Assignment 1 -- Basic Probability, Computing and Statistics 2015}

\author{}
\date{To be handed in at latest on Monday, September 7th}

\begin{document}
\maketitle

\paragraph{Exercises}

\begin{enumerate}
	\item If you flip a fair coin 6 times, what is the probability of getting exactly 4 tails?
	\item There are 11 students in a class: 4 boys and 7 girls. If you pick a group of 5 at random, what is the probability that everyone in the group is a girl?
	\item You have 6 friends, and want to pick and order 5 of them in a single line. In how many ways can you arrange them?
	\item How many functions defined on $n$ points are possible if each function can take a value from a set $V$?
	\item Ten students are to be divided into two cohorts of 5 students each. How many different divisions are possible? 
	\item How many different signals, each consisting of 9 colored dots on a pole, can be made from a set of 4 orange dots, 3 purple dots, and 2 cyan dots if all poles of the same color are identical?
	\item In how many unique ways can the letters of a word with $n$ letters be arranged if it contains repetitions of one letter $p$ times, and repetitions of another letter $q$ times?
	\item A program committee of 3 men and 3 women is to be formed from a group of 8 women and 6 men How many different committee are possible if 2 of the men refuse to serve together?
	\item You have 3 books on complexity theory, 2 on probability theory, and 1 novel. In how many ways can these books be arranged on a bookshelf if the books on complexity theory must be together but the other books can be arranged in any order?
	\item A restaurant is testing a new menu. They have prepared 3 tables with 2 distinct dishes for each table. If 3 sets of partners are to be assigned to these 6 dishes so that each partner tastes a different dish at the same table, how many assignments are possible?
	\item[*] In how many unique ways can the letters in the word `error' be arranged?
	\item[*] Jouke is packing his bags to go on vacation. He has 6 unique shirts, but only 5 fit in his bag. How many different groups of shirts does he have to chose from?
	\item[*] You got a free ticket for a guided bike tour to Bloemendal, and you can bring along 3 friends! Unfortunately, you have 7 who want to tag along on this exciting adventure. How many different groups of friends could you take with you?
	\item[*] How many functions defined on $n$ points are possible if each functional value is either $0$ or $1$?
	\item[*] A programme committee of $3$ is to be formed from a group of 20 reluctant researchers. How many different committees are possible?
\end{enumerate}



\end{document}
